Supplement to Global Distribution of Unintended Pregnancies and Contraceptive Usage Project

### 2024-05-02 products/manuscript/supplement/Supplementary-Material.qmd
Fixed error message on line 346 in supplementary.qmd

We explored the distribution of the countries by five categorical variables: `region`, `larcster_usage`, `sarc_usage`, `trad_usage`, and `none_usage` which is displayed in @tbl-summarytable1. These variables were not used in the main final analysi of the paper. We found that most countries are located in Africa followed by Asia and Latin America/the Caribbean. Only 20 countries have high usage of long acting reversible and sterilization methods compared to 33 countries with high usage of short acting reversible and traditional methods. It is interesting that the distributions for short acting reversible method, traditional method, and no method usages are the same. 
```{r}
#| label: tbl-summarytable1
#| tbl-cap: "Summary table for categorical variables"
#| echo: FALSE
resulttable1 <- readRDS("../../results/tables/summarytablecat.rds")
kable(resulttable1)
```

>>>>

We explored the distribution of the countries by five categorical variables: `region`, `larcster_usage`, `sarc_usage`, `trad_usage`, and `none_usage` which is displayed in @tbl-summarytable1. These variables were not used in the main final analysi of the paper. We found that most countries are located in Africa followed by Asia and Latin America/the Caribbean. Only 20 countries have high usage of long acting reversible and sterilization methods compared to 33 countries with high usage of short acting reversible and traditional methods. It is interesting that the distributions for short acting reversible method, traditional method, and no method usages are the same. 
```{r}
#| label: tbl-summarytable1
#| tbl-cap: "Summary table for categorical variables"
#| echo: FALSE
resulttable1 <- here("results","tables","summarytable.cat")
kable(resulttable1)
```
